Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-13 ms/response_letter.Rmd

Dear Editors,

We hereby resubmit the manuscript (AJB-D-21-00391), “Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)” (Phisamai Maenpuen, Masatoshi Katabuchi, Yusuke Onoda, Cong Zhou, Jiao-Lin Zhang, Ya-Jun Chen).
We thank the associate editor and the reviewers for their careful attention to detail in our manuscript and for providing comments that have greatly improved the study.

Based on the comments, we have updated the manuscript to reflect the following:

1. To quantify the effect of leaf morphology (leaf tissue density, leaf area, leaf thickness) and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we have built a hierarchical Bayesian model.
This allows us to quantify when the whole-leaf LMA to leaf disc LMA ratio become large and in which direction the relationship is changing.

2. We have removed the analysis that grouped species into four categories based on medians of leaf area and leaf thickness because it is somewhat arbitral as pointed by the reviewer.
Instead, the above Bayesian model was used to test our hypotheses.

3. We have also removed the individual-based analysis from the main text because variance among species are not independent in the individual-level data, and thus SMA or OLS regressions are not appropriate.
Analyses of individual-level data requires mixed linear models with species-level errors, but this is not useful for the context of our paper.
We therefore only report species-level results.

@@

> 1. Framing: I think the paper misses an opportunity to provide a bit more context for why the study is important. The authors could provide more concrete examples of why standardizing LMA techniques across studies matters: e.g. what is the ecological significance of an LMA measurement difference between the two methods?  This could also be set up in the introduction by providing more context for LMA as a functional trait. For example, by citing the TRY database, the authors could provide readers with the importance and ubiquity of LMA relative to other plant traits (e.g. of all the studies of plant traits in TRY, how many report LMA?)

Thank you.
We now note that a key difference between leaf disc and whole-leaf LMA is that leaf disc LMA focuses on lamina rather than whole-leaf and usages depend on ecological contexts (Line 75-77).
We also have mentioned the TRY database to explain LMA is the most often used leaf trait in TRY (Line 59-63).

> 2. A crucial thing for readers to know is how to "convert" one method's estimate of LMA to another: the authors could report an equation (or a few, accounting for some additional covariates such as leaf area and leaf thickness, which this paper identifies as important modifiers of the relationship) that scholars could use in the future if trying to compare LMA estimates collected using different methods. In other words, taking the eq from Appendix 2 and modifying it given the results of this study.

Thank you.
This is a good point and an important thing to clarify.
We now use a Bayesian model that includes leaf area and leaf thickness as covariates for both mean and variance.
However, we report several OLS models with and without leaf area in a practical guideline for LMA conversion (Line 303 - 323).

@@

Thank you.
We have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA (Line 104-111).
We now use Bao's CV estimator (CV4) instead of the coefficient of variation of log-normally distributed data ($CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}$).
We also limited to the analysis for species that have at least 5 individuals.
The relationship between the two estimates became much weaker (Fig. 4).

> Line comments:

> L49 I think the introduction would benefit from an initial sentence to give more context for the definition of LMA (perhaps by restructuring this paragraph to introduce traits and the LES first, and then defining LMA in that context).

Thank you.
We now introduce the LES in the first sentence so that the readers can understand the role of LMA in LES more clearly (Line 44-46).

@@

> L154-160 see major comment 3

Thank you.
We now use Bao's CV as noted above.

> L169-172 This is the major result of the paper. I suggest making it the first line of the results section (however I would modify it to fit the individual, rather than species-mean, level data: see below).

Thank you.
We have started the result section with the shift in elevation between whole-leaf and leaf disc LMA (i.e., whole-leaf LMA is greater than leaf disc LMA) (Line 234-).
Please see our response for using species- vs. individual-level data below.

@@

> Lin, S., Shao, L., Hui, C., Song, Y., Reddy, G.V.P., Gielis, J., Li, F., Ding, Y., Wei, Q., Shi, P. 2018. Why does not the leaf weight-area allometry of bamboos follow the 3/2-power law? Frontiers in Plant Science 9: 583, https://doi.org/10.1016/10.3389/fpls.2018.00583

Thank you.
We originally had this result to support grouping species into four categories, because if the correlation between leaf area and leaf thickness are too strong, we cannot group species into four categories based on median values of traits.
As noted above, we removed the analysis of grouping species, and thus we also removed this result.

> Line 171: "… were 9.4% greater than disc-based estimates …" Can you provide a standard deviation or a confidence interval for 9.4%? In general, we can use the bootstrap method to get it.

Thank you.
We have added confidence intervals using bootstraps in the result section (Line 252-255).

### 2022-05-13 ms/response_letter.Rmd

> L49 I think the introduction would benefit from an initial sentence to give more context for the definition of LMA (perhaps by restructuring this paragraph to introduce traits and the LES first, and then defining LMA in that context).

Thank you.
We now introduce the LES in the first sentence so that the readers can understand the role of LMA in LES more clearly (Line 44-46).

> L69-73 This sentence is crucial for your hypotheses but is buried in the middle of this paragraph. I suggest breaking this paragraph (beginning on line 63) up into 2: the first describing different methods of measurement and how commonly each are used, and any previous attempts to compare them. The second paragraph can get into which leaf types are likely to give similar or different estimates based on the two metrics and why.

Thank you.
We now break up the paragraph into two sections: the first describing the different methods and their record numbers in TRY, and previous works that compared them (Line 64-86), and the second describing the expected effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA (Line 87-103).

### 2022-05-18 report.Rmd
clean al

```{r}
tar_load(sp_mean)
sp_mean |>
  group_by(ldlalt_gr) |>
  summarise(
    lma_leaf = mean(lma_leaf) |> round(1),
    lma_disc = mean(lma_disc) |> round(1)
  ) |>
  write_csv("data/ldlalt.csv")
```

# Leaf disc vs whole-leaf LMA (species-level)

## Pooled

<!-- I put tar_load to use {{targets}} -->

```{r, include=FALSE}
tar_load(lalt_pool_grid_png)
```

![](figs/lalt_pool_grid.png)

## Seprated

```{r, include=FALSE}
tar_load(lalt_sep_grid_png)
```

## MCMC check

```{r,eval=TRUE}

targets::tar_load(fit_sp_no_lma_summary_model)
targets::tar_load(fit_sp_no_lma_int_summary_model)
targets::tar_load(fit_sp_lma_summary_model)
targets::tar_load(fit_sp_lma2_summary_model2)
targets::tar_load(fit_sp_ld_summary_model)
targets::tar_load(fit_sp_ld2_summary_model2)
targets::tar_load(fit_sp_ld3_summary_model)
targets::tar_load(fit_sp_lm_summary_model)
targets::tar_load(fit_sp_lma0_summary_simple)

targets::tar_load(fit_sp_no_lma_diagnostics_model)
targets::tar_load(fit_sp_no_lma_int_diagnostics_model)
targets::tar_load(fit_sp_lma_diagnostics_model)
targets::tar_load(fit_sp_lma2_diagnostics_model2)
targets::tar_load(fit_sp_ld_diagnostics_model)
targets::tar_load(fit_sp_ld2_diagnostics_model2)
targets::tar_load(fit_sp_ld3_diagnostics_model)
targets::tar_load(fit_sp_lm_diagnostics_model)
targets::tar_load(fit_sp_lma0_diagnostics_simple)
```

```{r,eval=TRUE}
fit_sp_no_lma_summary_model |> filter(rhat > 1.1)
fit_sp_no_lma_int_summary_model |> filter(rhat > 1.1)
fit_sp_lma_summary_model |> filter(rhat > 1.1)
fit_sp_lma2_summary_model2 |> filter(rhat > 1.1)
fit_sp_ld_summary_model |> filter(rhat > 1.1)
fit_sp_ld2_summary_model2 |> filter(rhat > 1.1)
fit_sp_ld3_summary_model |> filter(rhat > 1.1)
fit_sp_lm_summary_model |> filter(rhat > 1.1)
fit_sp_lma0_summary_simple |> filter(rhat > 1.1)
```

@@

```{r,eval=TRUE}
div_check(fit_sp_no_lma_diagnostics_model)
div_check(fit_sp_no_lma_int_diagnostics_model)
div_check(fit_sp_lma_diagnostics_model)
div_check(fit_sp_lma2_diagnostics_model2)
div_check(fit_sp_ld_diagnostics_model)
div_check(fit_sp_ld2_diagnostics_model2)
div_check(fit_sp_ld3_diagnostics_model)
div_check(fit_sp_lm_diagnostics_model)
div_check(fit_sp_lma0_diagnostics_simple)
```

```{r}
targets::tar_load(loo_model)
loo::loo_compare(
  loo_model[[1]], loo_model[[2]], loo_model[[3]],
  loo_model[[4]], loo_model[[5]], loo_model[[6]],
  loo_model[[7]], loo_model[[8]], loo_model[[9]],
  loo_model[[10]], loo_model[[11]],
  loo_model[[12]], loo_model[[13]]
)
```

@@

# SMA table

## species

```{r, eval=TRUE}
tar_load(sma_sp_tab)
sma_sp_tab |>
  kable() |>
  kable_styling()
```
```{r}
sma_sp_tab |>
  write_csv("data/sma_sp_tab.csv")
```

## species LD

```{r, eval=TRUE}
tar_load(sma_sp_ld_tab)
sma_sp_ld_tab |>
  kable() |>
  kable_styling()
```

```{r}
sma_sp_ld_tab |>
  write_csv("data/sma_sp_ld_tab.csv")
```

## species simple

```{r, eval=TRUE}
tar_load(sma_sp_2_tab)
sma_sp_2_tab |>
  kable() |>
  kable_styling()
```

```{r}
sma_sp_2_tab |>
  write_csv("data/sma_sp_2_tab.csv")
```

## tree

```{r, eval=TRUE}
tar_load(sma_tree_tab)
sma_tree_tab |>
  kable() |>
  kable_styling()
```

## tree LD

```{r, eval=TRUE}
tar_load(sma_tree_ld_tab)
sma_tree_ld_tab |>
  kable() |>
  kable_styling()
```

@@

```{r}
tar_load(cv_tree)
cv_tree
```

# Leaf disc vs whole-leaf LMA (individual-level)

```{r, include=FALSE}
tar_load(lalt_tree_grid_png)
```

![](figs/lalt_tree_grid.png)

# Divergence (species-level)

```{r, include=FALSE}
tar_load(ratio_png)
```

![](figs/ratio.png)

@@

```{r, include=FALSE}
tar_load(lma_ld_png)
```

@@

```{r, include=FALSE}
tar_load(cv_pool_png)
```

@@

```{r, include=FALSE}
tar_load(cv_sep_png)
```

![](figs/cv_sep.png)

@@

```{r, include=FALSE}
tar_load(petiole_png)
```

@@

@@

```{r}
tar_visnetwork()
```

>>>>

# MCMC check

```{r,eval=TRUE}
targets::tar_load(fit_sp_no_lma_summary_model)
targets::tar_load(fit_sp_no_lma_int_summary_model)
targets::tar_load(fit_sp_lma_summary_model)
targets::tar_load(fit_sp_lma2_summary_model2)
targets::tar_load(fit_sp_ld_summary_model)
targets::tar_load(fit_sp_ld3_summary_model)
targets::tar_load(fit_sp_lm_summary_model)
targets::tar_load(fit_sp_lma0_summary_simple)

targets::tar_load(fit_sp_no_lma_diagnostics_model)
targets::tar_load(fit_sp_no_lma_int_diagnostics_model)
targets::tar_load(fit_sp_lma_diagnostics_model)
targets::tar_load(fit_sp_lma2_diagnostics_model2)
targets::tar_load(fit_sp_ld_diagnostics_model)
targets::tar_load(fit_sp_ld3_diagnostics_model)
targets::tar_load(fit_sp_lm_diagnostics_model)
targets::tar_load(fit_sp_lma0_diagnostics_simple)
```

```{r,eval=TRUE}
fit_sp_no_lma_summary_model |> filter(rhat > 1.1)
fit_sp_no_lma_int_summary_model |> filter(rhat > 1.1)
fit_sp_lma_summary_model |> filter(rhat > 1.1)
fit_sp_lma2_summary_model2 |> filter(rhat > 1.1)
fit_sp_ld_summary_model |> filter(rhat > 1.1)
fit_sp_ld3_summary_model |> filter(rhat > 1.1)
fit_sp_lm_summary_model |> filter(rhat > 1.1)
fit_sp_lma0_summary_simple |> filter(rhat > 1.1)
```

@@

```{r,eval=TRUE}
div_check(fit_sp_no_lma_diagnostics_model)
div_check(fit_sp_no_lma_int_diagnostics_model)
div_check(fit_sp_lma_diagnostics_model)
div_check(fit_sp_lma2_diagnostics_model2)
div_check(fit_sp_ld_diagnostics_model)
div_check(fit_sp_ld3_diagnostics_model)
div_check(fit_sp_lm_diagnostics_model)
div_check(fit_sp_lma0_diagnostics_simple)
```

```{r}
targets::tar_load(loo_model)
loo::loo_compare(
  loo_model[[1]], loo_model[[2]], loo_model[[3]],
  loo_model[[4]], loo_model[[5]], loo_model[[6]],
  loo_model[[7]], loo_model[[8]], loo_model[[9]],
  loo_model[[10]], loo_model[[11]])
```

@@

``

@@

@@

```{r, include=FALSE}
tar_load(lma_ld_plot)
```

@@

```{r, include=FALSE}
tar_load(cv_pool_plot)
```

@@

@@

```{r, include=FALSE}
tar_load(petiole_plot)
```

@@

# DM and HDK

```{r}
tar_load(tree)
fit <- lm(log(lma_leaf / lma_disc) ~ log(dry_mass_disc), tree)
lmtest::bptest(fit)
```

# {targets} pipepline

```{r}
targets::tar_visnetwork()
```

@@
